Abstractions for Multi-Sorted Substitutions

### 2023-09-15 paper/paper.tex
Update.

  Next we define \ACode{\ACon{TypingKit}}s, which are analog to
  \ACode{\ACon{Kit}}s, but abstract about variable and term
  \emph{typing}, instead of variables and terms, themselves.
  \LibCode\KTypingKit
  Building on the fields of a \ACode{\ACon{TypingKit}}, we define further operations:
  \begin{itemize}
  \item
    Using the variable/term typing, we can define a renaming/substitution typing:
    \LibCode\KMapTyping
  \item 
    Lifting a map preserves its typing:
    \LibCode\KLiftTyping
    % \LibCode\KLiftTypingProof
  \item 
    If a variable/term has a typing, then so does its singleton renaming/substitution:
    \LibCode\KSingleTyping
    % \LibCode\KSingleTypingProof
  \end{itemize}
  We also specify notation, which makes it less cumbersome
  to explicitly pass a particular Kit to those definitions:
  \begin{itemize}
  \item \ACode{Γ₂ \ADef{∋*/⊢*[} TK \ADef{]} ϕ \ADef{∶} Γ₁} is
    \ACode{Γ₂ \ADef{∋*/⊢*} ϕ \ADef{∶} Γ₁} for some \ACode{\ACon{TypingKit}} \ACode{TK}.
  \end{itemize}
  % \LibCode\KTypingNotation

  We then define a \ACode{\ACon{TypingTraversal}} analogously to
  \ACode{\ACon{Traversal}}, but instead of defining the application of
  renamings/substitutions, it defines the type preservation of applying
  renamings/substitutions:
  \LibCode\KTypingTraversal
  \LibCode\KTypingInstances
  % \LibCode\KTypingTraversalNotation
  \subsection{System F}
  \AppCode\FPreserve
  \AppCode\FTypingTraversal

>>>>

  Next we define \ACode{\ACon{TypingKit}}s, which are analog to
  \ACode{\ACon{Kit}}s, but abstract about variable and term
  \emph{typing}, instead of variables and terms, themselves.
  \LibCode\KTypingKit
  Building on the fields of a \ACode{\ACon{TypingKit}}, we define further operations:
  \begin{itemize}
  \item
    Using the variable/term typing, we can define a renaming/substitution typing:
    \LibCode\KMapTyping
  \item 
    Lifting a map preserves its typing:
    \LibCode\KLiftTyping
    % \LibCode\KLiftTypingProof
  \item 
    If a variable/term has a typing, then so does its singleton renaming/substitution:
    \LibCode\KSingleTyping
    % \LibCode\KSingleTypingProof
  \end{itemize}
  To make it easier to explicitly pass typing kits,
  we define the notation \ACode{Γ₂ \ADef{∋*/⊢*[} TK \ADef{]} ϕ \ADef{∶} Γ₁}
  to stand for \ACode{Γ₂ \ADef{∋*/⊢*} ϕ \ADef{∶} Γ₁} given some
  \ACode{\ACon{TypingKit}} \ACode{TK}.
  % \LibCode\KTypingNotation

  We then define a \ACode{\ACon{TypingTraversal}} analogously to
  \ACode{\ACon{Traversal}}, but instead of defining the application of
  maps, it defines the type preservation of applying maps:
  \LibCode\KTypingTraversal
  Given a variable/term \ACode{e} with typing \ACode{⊢e} and
  a renaming/substitution \ACode{ϕ} with typing \ACode{⊢ϕ},
  the term \ACode{⊢e \AField{⊢⋯} ⊢ϕ} is a typing for \ACode{e \AField{⋯} ϕ}.

  Given a \ACode{\ACon{TypingTraversal}}, we can easily instanciate the
  \ACode{\ACon{TypingKits}} for variables and terms:
  \LibCode\KTypingInstances
  % \LibCode\KTypingTraversalNotation

  We are then ready to create a \ACode{\ACon{TypingTraversal}}
  instance for System F:
  \AppCode\FPreserve
  \AppCode\FTypingTraversal
